---
title: "Lab 09: Algorithmic Bias"
author: "Benjamin Egan"
date: "3/26/25"
output: github_document
---

Here is the link to the assignment page: https://datascience4psych.github.io/DataScience4Psych/lab09.html. This includes the relevant information for the assignment alongside required questions I needed to answer.

```{r load-packages, message = FALSE, echo = FALSE}
library(tidyverse)
library(fairness)
```

### The data

For this lab, we'll use the COMPAS dataset compiled by ProPublica. The data has been preprocessed and cleaned for you. You'll have to load it yourself. The dataset is available in the `data` folder, but I've changed the file name from `compas-scores-two-years.csv` to `compas-scores-2-years.csv`. I've done this help you practice debugging code when you encounter an error.

```{r load dataset}
compas <- read_csv("data/compas-scores-2-years.csv")
```


## Additional Exercises  

Almost there! Keep building on your work and follow the same structure for any remaining exercises. Each exercise builds on the last, so take your time and make sure your code is working as expected.  
